### 2019-09-04 paper/HOLMultivariate.tex
Improved TeX output of "nil" (final changes on HOL side)

\newcommand{\HOLMultivariateTime}{10:49}

@@

       \HOLConst{ALL_DISTINCT} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} (\HOLConst{LENGTH} \HOLBoundVar{Es} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenConj{}}
       \HOLConst{EVERY} (\HOLTokenLambda{}\HOLBoundVar{e}. \HOLConst{FV} \HOLBoundVar{e} \HOLConst{\HOLTokenSubset{}} \HOLConst{set} \HOLBoundVar{Xs}) \HOLBoundVar{Es}

@@

       \HOLConst{ALL_PROC} \HOLBoundVar{Ps} \HOLSymConst{\HOLTokenConj{}} \HOLConst{EVERY} (\HOLTokenLambda{}\HOLBoundVar{e}. \HOLConst{DISJOINT} (\HOLConst{BV} \HOLBoundVar{e}) (\HOLConst{set} \HOLBoundVar{Xs})) \HOLBoundVar{Ps} \HOLSymConst{\HOLTokenConj{}}
       \HOLConst{LIST_REL} \HOLBoundVar{R} \HOLBoundVar{Ps} (\HOLConst{MAP} [\HOLBoundVar{Ps}/\HOLBoundVar{Xs}] \HOLBoundVar{Es})

@@

\HOLTokenTurnstile{} (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{fm}. \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLConst{nil} \HOLSymConst{=} \HOLConst{nil}) \HOLSymConst{\HOLTokenConj{}}
   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{fm} \HOLBoundVar{u} \HOLBoundVar{E}. \HOLConst{CCS_SUBST} \HOLBoundVar{fm} (\HOLBoundVar{u}\HOLSymConst{..}\HOLBoundVar{E}) \HOLSymConst{=} \HOLBoundVar{u}\HOLSymConst{..}\HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E}) \HOLSymConst{\HOLTokenConj{}}
   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{fm} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}.
        \HOLConst{CCS_SUBST} \HOLBoundVar{fm} (\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{E\sb{\mathrm{2}}}) \HOLSymConst{=}
        \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E\sb{\mathrm{2}}}) \HOLSymConst{\HOLTokenConj{}}
   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{fm} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}.
        \HOLConst{CCS_SUBST} \HOLBoundVar{fm} (\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\parallel}} \HOLBoundVar{E\sb{\mathrm{2}}}) \HOLSymConst{=}
        \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\parallel}} \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E\sb{\mathrm{2}}}) \HOLSymConst{\HOLTokenConj{}}
   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{fm} \HOLBoundVar{L} \HOLBoundVar{E}. \HOLConst{CCS_SUBST} \HOLBoundVar{fm} (\HOLConst{\ensuremath{\nu}} \HOLBoundVar{L} \HOLBoundVar{E}) \HOLSymConst{=} \HOLConst{\ensuremath{\nu}} \HOLBoundVar{L} (\HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E})) \HOLSymConst{\HOLTokenConj{}}
   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{fm} \HOLBoundVar{E} \HOLBoundVar{rf}.
        \HOLConst{CCS_SUBST} \HOLBoundVar{fm} (\HOLConst{relab} \HOLBoundVar{E} \HOLBoundVar{rf}) \HOLSymConst{=} \HOLConst{relab} (\HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E}) \HOLBoundVar{rf}) \HOLSymConst{\HOLTokenConj{}}
   (\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{fm} \HOLBoundVar{X}.
        \HOLConst{CCS_SUBST} \HOLBoundVar{fm} (\HOLConst{var} \HOLBoundVar{X}) \HOLSymConst{=}
        \HOLKeyword{if} \HOLBoundVar{X} \HOLConst{\HOLTokenIn{}} \HOLConst{FDOM} \HOLBoundVar{fm} \HOLKeyword{then} \HOLBoundVar{fm} \HOLConst{'} \HOLBoundVar{X} \HOLKeyword{else} \HOLConst{var} \HOLBoundVar{X}) \HOLSymConst{\HOLTokenConj{}}

@@

       \HOLConst{CCS_SUBST} \HOLBoundVar{fm} (\HOLConst{rec} \HOLBoundVar{X} \HOLBoundVar{E}) \HOLSymConst{=}
       \HOLKeyword{if} \HOLBoundVar{X} \HOLConst{\HOLTokenIn{}} \HOLConst{FDOM} \HOLBoundVar{fm} \HOLKeyword{then} \HOLConst{rec} \HOLBoundVar{X} (\HOLConst{CCS_SUBST} (\HOLBoundVar{fm} \HOLSymConst{\ensuremath{\setminus}} \HOLBoundVar{X}) \HOLBoundVar{E})
       \HOLKeyword{else} \HOLConst{rec} \HOLBoundVar{X} (\HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E})

@@

       \HOLConst{context} \HOLBoundVar{Xs} \HOLSymConst{=}
       (\HOLTokenLambda{}\HOLBoundVar{E}.
            \HOLConst{DISJOINT} (\HOLConst{BV} \HOLBoundVar{E}) (\HOLConst{set} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenConj{}}
            \HOLConst{EVERY} (\HOLTokenLambda{}\HOLBoundVar{X}. \HOLConst{CONTEXT} (\HOLTokenLambda{}\HOLBoundVar{t}. [\HOLBoundVar{t}/\HOLBoundVar{X}] \HOLBoundVar{E})) \HOLBoundVar{Xs})

@@

\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Ps}. \HOLConst{fromList} \HOLBoundVar{Xs} \HOLBoundVar{Ps} \HOLSymConst{=} \HOLConst{FEMPTY} \HOLSymConst{|++} \HOLConst{ZIP} (\HOLBoundVar{Xs}\HOLSymConst{,}\HOLBoundVar{Ps})

@@

       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLSymConst{=}
       (\HOLTokenLambda{}\HOLBoundVar{E}.
            \HOLConst{DISJOINT} (\HOLConst{BV} \HOLBoundVar{E}) (\HOLConst{set} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenConj{}}
            \HOLConst{EVERY} (\HOLTokenLambda{}\HOLBoundVar{X}. \HOLConst{WG} (\HOLTokenLambda{}\HOLBoundVar{t}. [\HOLBoundVar{t}/\HOLBoundVar{X}] \HOLBoundVar{E})) \HOLBoundVar{Xs})

@@

       \HOLConst{ALL_DISTINCT} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} (\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenConj{}}
       \HOLConst{DISJOINT} (\HOLConst{BV} \HOLBoundVar{E}) (\HOLConst{set} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenImp{}}
       \HOLConst{BV} ([\HOLBoundVar{Ps}/\HOLBoundVar{Xs}] \HOLBoundVar{E}) \HOLConst{\HOLTokenSubset{}} \HOLConst{BV} \HOLBoundVar{E} \HOLConst{\HOLTokenUnion{}} \HOLConst{BIGUNION} (\HOLConst{IMAGE} \HOLConst{BV} (\HOLConst{set} \HOLBoundVar{Ps}))

@@

       (\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs})

@@

       \HOLConst{DISJOINT} (\HOLConst{FV} \HOLBoundVar{E}) (\HOLConst{set} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenConj{}} (\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenImp{}}
       ([\HOLBoundVar{Ps}/\HOLBoundVar{Xs}] \HOLBoundVar{E} \HOLSymConst{=} \HOLBoundVar{E})

@@

\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{fm}. \HOLConst{DISJOINT} (\HOLConst{FV} \HOLBoundVar{E}) (\HOLConst{FDOM} \HOLBoundVar{fm}) \HOLSymConst{\HOLTokenImp{}} (\HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E} \HOLSymConst{=} \HOLBoundVar{E})

@@

\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E}. \HOLConst{CCS_SUBST} \HOLConst{FEMPTY} \HOLBoundVar{E} \HOLSymConst{=} \HOLBoundVar{E}

@@

       \HOLConst{ALL_DISTINCT} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} (\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenConj{}}
       \HOLConst{EVERY} (\HOLTokenLambda{}(\HOLBoundVar{x}\HOLSymConst{,}\HOLBoundVar{p}). \HOLConst{FV} \HOLBoundVar{p} \HOLConst{\HOLTokenSubset{}} \HOLTokenLeftbrace{}\HOLBoundVar{x}\HOLTokenRightbrace{}) (\HOLConst{ZIP} (\HOLBoundVar{Xs}\HOLSymConst{,}\HOLBoundVar{Ps})) \HOLSymConst{\HOLTokenConj{}}
       \HOLConst{DISJOINT} (\HOLConst{BV} \HOLBoundVar{E}) (\HOLConst{set} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenImp{}}
       ([\HOLBoundVar{Ps}/\HOLBoundVar{Xs}] \HOLBoundVar{E} \HOLSymConst{=} \HOLConst{FOLDR} (\HOLTokenLambda{}(\HOLBoundVar{x}\HOLSymConst{,}\HOLBoundVar{y}) \HOLBoundVar{e}. [\HOLBoundVar{y}/\HOLBoundVar{x}] \HOLBoundVar{e}) \HOLBoundVar{E} (\HOLConst{ZIP} (\HOLBoundVar{Xs}\HOLSymConst{,}\HOLBoundVar{Ps})))

@@

       \HOLConst{ALL_DISTINCT} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} (\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenConj{}} \HOLConst{ALL_PROC} \HOLBoundVar{Ps} \HOLSymConst{\HOLTokenConj{}}
       \HOLConst{FV} \HOLBoundVar{E} \HOLConst{\HOLTokenSubset{}} \HOLConst{set} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} (\HOLConst{BV} \HOLBoundVar{E}) (\HOLConst{set} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenImp{}}
       \HOLConst{IS_PROC} ([\HOLBoundVar{Ps}/\HOLBoundVar{Xs}] \HOLBoundVar{E})

@@

       \HOLConst{ALL_DISTINCT} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} (\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenConj{}}
       (\HOLConst{LENGTH} \HOLBoundVar{Es} \HOLSymConst{=} \HOLConst{LENGTH} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} (\HOLConst{BV} \HOLBoundVar{C}) (\HOLConst{set} \HOLBoundVar{Xs}) \HOLSymConst{\HOLTokenImp{}}
       ([\HOLBoundVar{Ps}/\HOLBoundVar{Xs}] ([\HOLBoundVar{Es}/\HOLBoundVar{Xs}] \HOLBoundVar{C}) \HOLSymConst{=} [\HOLConst{MAP} [\HOLBoundVar{Ps}/\HOLBoundVar{Xs}] \HOLBoundVar{Es}/\HOLBoundVar{Xs}] \HOLBoundVar{C})

@@

\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{fm}. \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLConst{nil} \HOLSymConst{=} \HOLConst{nil}

@@

       \HOLConst{CCS_SUBST} \HOLBoundVar{fm} (\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\parallel}} \HOLBoundVar{E\sb{\mathrm{2}}}) \HOLSymConst{=}
       \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\parallel}} \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E\sb{\mathrm{2}}}

@@

       ([\HOLBoundVar{Ps}/\HOLBoundVar{Xs}] \HOLBoundVar{P} \HOLSymConst{=} \HOLBoundVar{P})

>>>>

\newcommand{\HOLMultivariateTime}{13:47}

@@

       \HOLConst{ALL_DISTINCT} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLConst{LENGTH} \HOLBoundVar{Es} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
       \HOLConst{EVERY} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{e}. \HOLConst{FV} \HOLBoundVar{e} \HOLConst{\HOLTokenSubset{}} \HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLBoundVar{Es}

@@

       \HOLConst{ALL_PROC} \HOLBoundVar{Ps} \HOLSymConst{\HOLTokenConj{}} \HOLConst{EVERY} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{e}. \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{e}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)}\ensuremath{)} \HOLBoundVar{Ps} \HOLSymConst{\HOLTokenConj{}}
       \HOLConst{LIST_REL} \HOLBoundVar{R} \HOLBoundVar{Ps} \ensuremath{(}\HOLConst{MAP} \ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{Es}\ensuremath{)}

@@

\HOLTokenTurnstile{} \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{fm}. \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLConst{\ensuremath{\mathbf{0}}} \HOLSymConst{\ensuremath{=}} \HOLConst{\ensuremath{\mathbf{0}}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{fm} \HOLBoundVar{u} \HOLBoundVar{E}. \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \ensuremath{(}\HOLBoundVar{u}\HOLSymConst{\ensuremath{\ldotp}}\HOLBoundVar{E}\ensuremath{)} \HOLSymConst{\ensuremath{=}} \HOLBoundVar{u}\HOLSymConst{\ensuremath{\ldotp}}\HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{fm} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}.
        \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \ensuremath{(}\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \HOLBoundVar{E\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\ensuremath{=}}
        \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{+}} \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{fm} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLBoundVar{E\sb{\mathrm{2}}}.
        \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \ensuremath{(}\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\mid}} \HOLBoundVar{E\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\ensuremath{=}}
        \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\mid}} \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{fm} \HOLBoundVar{L} \HOLBoundVar{E}. \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \ensuremath{(}\HOLConst{nu} \HOLBoundVar{L} \HOLBoundVar{E}\ensuremath{)} \HOLSymConst{\ensuremath{=}} \HOLConst{nu} \HOLBoundVar{L} \ensuremath{(}\HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{fm} \HOLBoundVar{E} \HOLBoundVar{rf}.
        \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \ensuremath{(}\HOLConst{relab} \HOLBoundVar{E} \HOLBoundVar{rf}\ensuremath{)} \HOLSymConst{\ensuremath{=}} \HOLConst{relab} \ensuremath{(}\HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E}\ensuremath{)} \HOLBoundVar{rf}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
   \ensuremath{(}\HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{fm} \HOLBoundVar{X}.
        \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \ensuremath{(}\HOLConst{var} \HOLBoundVar{X}\ensuremath{)} \HOLSymConst{\ensuremath{=}}
        \HOLKeyword{if} \HOLBoundVar{X} \HOLConst{\HOLTokenIn{}} \HOLConst{FDOM} \HOLBoundVar{fm} \HOLKeyword{then} \HOLBoundVar{fm} \HOLConst{'} \HOLBoundVar{X} \HOLKeyword{else} \HOLConst{var} \HOLBoundVar{X}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}

@@

       \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \ensuremath{(}\HOLConst{rec} \HOLBoundVar{X} \HOLBoundVar{E}\ensuremath{)} \HOLSymConst{\ensuremath{=}}
       \HOLKeyword{if} \HOLBoundVar{X} \HOLConst{\HOLTokenIn{}} \HOLConst{FDOM} \HOLBoundVar{fm} \HOLKeyword{then} \HOLConst{rec} \HOLBoundVar{X} \ensuremath{(}\HOLConst{CCS_SUBST} \ensuremath{(}\HOLBoundVar{fm} \HOLSymConst{\ensuremath{\setminus}} \HOLBoundVar{X}\ensuremath{)} \HOLBoundVar{E}\ensuremath{)}
       \HOLKeyword{else} \HOLConst{rec} \HOLBoundVar{X} \ensuremath{(}\HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E}\ensuremath{)}

@@

       \HOLConst{context} \HOLBoundVar{Xs} \HOLSymConst{\ensuremath{=}}
       \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{E}.
            \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
            \HOLConst{EVERY} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{X}. \HOLConst{CONTEXT} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \ensuremath{[}\HOLBoundVar{t}\ensuremath{/}\HOLBoundVar{X}\ensuremath{]} \HOLBoundVar{E}\ensuremath{)}\ensuremath{)} \HOLBoundVar{Xs}\ensuremath{)}

@@

\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Xs} \HOLBoundVar{Ps}. \HOLConst{fromList} \HOLBoundVar{Xs} \HOLBoundVar{Ps} \HOLSymConst{\ensuremath{=}} \HOLConst{FEMPTY} \HOLSymConst{|++} \HOLConst{ZIP} \ensuremath{(}\HOLBoundVar{Xs}\HOLSymConst{,}\HOLBoundVar{Ps}\ensuremath{)}

@@

       \HOLConst{weakly_guarded} \HOLBoundVar{Xs} \HOLSymConst{\ensuremath{=}}
       \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{E}.
            \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
            \HOLConst{EVERY} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{X}. \HOLConst{WG} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{t}. \ensuremath{[}\HOLBoundVar{t}\ensuremath{/}\HOLBoundVar{X}\ensuremath{]} \HOLBoundVar{E}\ensuremath{)}\ensuremath{)} \HOLBoundVar{Xs}\ensuremath{)}

@@

       \HOLConst{ALL_DISTINCT} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
       \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
       \HOLConst{BV} \ensuremath{(}\ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{E}\ensuremath{)} \HOLConst{\HOLTokenSubset{}} \HOLConst{BV} \HOLBoundVar{E} \HOLConst{\HOLTokenUnion{}} \HOLConst{BIGUNION} \ensuremath{(}\HOLConst{IMAGE} \HOLConst{BV} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Ps}\ensuremath{)}\ensuremath{)}

@@

       \ensuremath{(}\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLBoundVar{Xs}\ensuremath{)}

@@

       \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{FV} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
       \ensuremath{(}\ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{E} \HOLSymConst{\ensuremath{=}} \HOLBoundVar{E}\ensuremath{)}

@@

\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E} \HOLBoundVar{fm}. \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{FV} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{FDOM} \HOLBoundVar{fm}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}} \ensuremath{(}\HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E} \HOLSymConst{\ensuremath{=}} \HOLBoundVar{E}\ensuremath{)}

@@

\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{E}. \HOLConst{CCS_SUBST} \HOLConst{FEMPTY} \HOLBoundVar{E} \HOLSymConst{\ensuremath{=}} \HOLBoundVar{E}

@@

       \HOLConst{ALL_DISTINCT} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
       \HOLConst{EVERY} \ensuremath{(}\HOLTokenLambda{}\ensuremath{(}\HOLBoundVar{x}\HOLSymConst{,}\HOLBoundVar{p}\ensuremath{)}. \HOLConst{FV} \HOLBoundVar{p} \HOLConst{\HOLTokenSubset{}} \HOLTokenLeftbrace{}\HOLBoundVar{x}\HOLTokenRightbrace{}\ensuremath{)} \ensuremath{(}\HOLConst{ZIP} \ensuremath{(}\HOLBoundVar{Xs}\HOLSymConst{,}\HOLBoundVar{Ps}\ensuremath{)}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
       \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
       \ensuremath{(}\ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{E} \HOLSymConst{\ensuremath{=}} \HOLConst{FOLDR} \ensuremath{(}\HOLTokenLambda{}\ensuremath{(}\HOLBoundVar{x}\HOLSymConst{,}\HOLBoundVar{y}\ensuremath{)} \HOLBoundVar{e}. \ensuremath{[}\HOLBoundVar{y}\ensuremath{/}\HOLBoundVar{x}\ensuremath{]} \HOLBoundVar{e}\ensuremath{)} \HOLBoundVar{E} \ensuremath{(}\HOLConst{ZIP} \ensuremath{(}\HOLBoundVar{Xs}\HOLSymConst{,}\HOLBoundVar{Ps}\ensuremath{)}\ensuremath{)}\ensuremath{)}

@@

       \HOLConst{ALL_DISTINCT} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \HOLConst{ALL_PROC} \HOLBoundVar{Ps} \HOLSymConst{\HOLTokenConj{}}
       \HOLConst{FV} \HOLBoundVar{E} \HOLConst{\HOLTokenSubset{}} \HOLConst{set} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
       \HOLConst{IS_PROC} \ensuremath{(}\ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{E}\ensuremath{)}

@@

       \HOLConst{ALL_DISTINCT} \HOLBoundVar{Xs} \HOLSymConst{\HOLTokenConj{}} \ensuremath{(}\HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
       \ensuremath{(}\HOLConst{LENGTH} \HOLBoundVar{Es} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{C}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLBoundVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
       \ensuremath{(}\ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \ensuremath{(}\ensuremath{[}\HOLBoundVar{Es}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{C}\ensuremath{)} \HOLSymConst{\ensuremath{=}} \ensuremath{[}\HOLConst{MAP} \ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{Es}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{C}\ensuremath{)}

@@

\HOLTokenTurnstile{} \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{fm}. \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLConst{\ensuremath{\mathbf{0}}} \HOLSymConst{\ensuremath{=}} \HOLConst{\ensuremath{\mathbf{0}}}

@@

       \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \ensuremath{(}\HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\mid}} \HOLBoundVar{E\sb{\mathrm{2}}}\ensuremath{)} \HOLSymConst{\ensuremath{=}}
       \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E\sb{\mathrm{1}}} \HOLSymConst{\ensuremath{\mid}} \HOLConst{CCS_SUBST} \HOLBoundVar{fm} \HOLBoundVar{E\sb{\mathrm{2}}}

@@

       \ensuremath{(}\ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLBoundVar{Xs}\ensuremath{]} \HOLBoundVar{P} \HOLSymConst{\ensuremath{=}} \HOLBoundVar{P}\ensuremath{)}
